---
title: "607-wk9-homework9"
author: "Tyler Frankenberg"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(jsonlite)

```

## Introduction

The *New York Times* API service at <https://api.nytimes.com> offers a wealth of information with relatively easy access to those who register as developers.

In this vignette we're going to connect to the API for the purpose of locating the current "Food and Nutrition" bestseller's list.

### Finding the appropriate list

We're interested in calling the API for the "Food and Nutrition" Bestseller's list, but in order to access this particular list we'll need to call the `lists/names` API so that we know which name to pass into the subsequent call...

```{r json}

key <- "dTCYJGGFC3MS59x7qXPoEkUxfuxcj4RH"

url <- paste("https://api.nytimes.com/svc/books/v3/lists/names.json?api-key=", key, sep = "")

nyt_lists <- jsonlite::fromJSON(url)

lists_df <- as.data.frame(nyt_lists$results)

lists_df

```
### Food and Fitness API

A little perusing of this `data.frame` shows that we're interested in row 41 - the list named "Food and Fitness."  We'll pass its value for `list_name_encoded` into the api-call URL which will give us what we're looking for...

```{r name}

url2 <- paste("https://api.nytimes.com/svc/books/v3/lists/current/food-and-fitness.json?api-key=", key, sep = "")

food_list <- jsonlite::fromJSON(url2)

food_df <- as.data.frame(food_list[[5]]$books)

food_df

```

